Replication in Archaeological Science: Shape as a Measure of Weapon Standardisation

### 2020-02-24 analysis/paper.Rmd
replicated ANOVA test

As of geomorph version 3.1, the function procD.allmoetry has been deprecated (see https://rdrr.io/cran/geomorph/man/procD.allometry.html). This function underpinned the ANOVA tests provided in the technical code appendix.

```{r replication ANOVA  test, include=TRUE, echo=FALSE}

# The results are significant, but they cannot be explained by site difference
#lances_ANOVA<-procD.allometry(shape ~ size, ~site, data=lances_geomorph,method="PredLine") 
lances_ANOVA<-procD.allometry(shape ~ size, data=lances_geomorph,method="PredLine")
rep_test <- procD.lm(shape ~ size,data=lances_geomorph,method="PredLine")
plot(rep_test)
plot(lances_ANOVA)

anova.lm.rrpp(fit.common, fit.unique)
?anova.lm.rrpp
?plotAllometry
#print(lances_ANOVA)

# simple allometry model
fit.size <- procD.lm(shape ~ size, 
                     data = lances_geomorph, print.progress = FALSE)
plot(fit.size, type = "regression", reg.type = "PredLine", predictor = lances_geomorph$size)
plot(fit.size, type = "regression", reg.type = "RegScore", predictor = lances_geomorph$size)
plot(lances_ANOVA)

PLS <- two.b.pls(lances_geomorph$shape, lances_geomorph$size, print.progress = FALSE)
PLS
plot(PLS)
```
## Methods

## Results

## Conclusion

## References

>>>>

As of geomorph version 3.1, the function procD.allmoetry has been deprecated (see https://rdrr.io/cran/geomorph/man/procD.allometry.html). This function underpinned the ANOVA tests provided in the technical code appendix. Thankfully, the specificity of the authors' instructions allow a previous version of geomorph to be installed!

wereplicate the results of p.44 on the ANOVA tests used to establish whether there is a significant relationship between centroid size and shape.

```{r replication ANOVA  test, include=TRUE, echo=FALSE}
lances_ANOVA_site<-procD.allometry(shape ~ size, ~site, data=lances_geomorph,method="PredLine")

print(lances_ANOVA_site)

The results match. We note that no seed is specified in the provided code, making the random resampling approach used volatile.
